\documentclass[english,master]{unibg}

\title{ScrapegraphAI : Data Scraping 2.0 }
\advisor{Chiar.mo Prof. Alessandro Fassò}
% \coadvisor{Chiar.mo Prof.~Ed Smith}

\department{Ingegneria Gestionale, dell'Informazione e della Produzione}
\course{Ingegneria Informatica}
\class{LM-32}

\author{Marco Vinciguerra}
\studentid{1064889}
\academicyear{2024/2025}

\begin{document}
\maketitle
\emptypage

\begin{abstract}
The rapid evolution of web scraping has led to increasing challenges in extracting structured information from dynamic and complex websites. This thesis presents ScrapegraphAI, a novel open-source library designed to redefine data extraction through Large Language Models (LLMs) and agent-based architectures.

This study examines the limitations of traditional web scraping techniques---such as CSS selectors, XPath, and API-based extraction---highlighting their inefficiencies in handling JavaScript-rendered content and adapting to evolving anti-bot policies.

ScrapegraphAI leverages Retrieval-Augmented Generation (RAG) and neural architectures to automate web scraping, reducing reliance on manual scripting while improving accuracy and adaptability.

The findings of this thesis suggest that AI-driven scraping paradigms can significantly enhance automation and data accessibility, paving the way for intelligent and resilient web crawlers. Future work will explore multi-agent collaboration, integration with Reinforcement Learning, and real-time document segmentation to optimize large-scale data retrieval.
\end{abstract}

\emptypage
\toc
\emptypage

\clearpage
\pagenumbering{arabic}

\input{chapters/chap01.tex}
\listoffigures
\listoftables

\bibliographystyle{siam}

\begin{thebibliography}{1}
\bibitem{1} Glez-Peña, Daniel, et al. "Web scraping technologies in an API world." Briefings in Bioinformatics 15.5 (2014): 788-797.

\bibitem{2}  
Dennis D. Hirsch,  
"The glass house effect: Big Data, the new oil, and the power of analogy,"  
\textit{Me. L. Rev.}, vol. 66, pp. 373, 2013.  

\bibitem{3} 
Dennis D. Hirsch, ``The Glass House Effect: Big Data, the New Oil, and the Power of Analogy,'' \textit{Maine Law Review}, vol. 66, no. 2, 2014, pp. 373-396.

\bibitem{4}
K. Decker, K. Sycara, and M. Williamson. Middle-agents for the Internet. In *Proceedings of the Fifteenth International Joint Conference on Artificial Intelligence (IJCAI)*, 1997.

\bibitem{5}
    S. Abar, G. K. Theodoropoulos, P. Lemarinier, and G. M. P. O’Hare, ``Agent Based Modelling and Simulation tools: A review of the state-of-art software,'' \emph{Computer Science Review}, vol. 24, pp. 13–33, 2017.

\bibitem{6} Azad, Babak Amin, et al. "Web Runner 2049: Evaluating Third-Party Anti-bot Services." \textit{DIMVA 2020, Lecture Notes in Computer Science}, vol. 12223, 2020, pp. 135–159. Springer, https://doi.org/10.1007/978-3-030-52683-2\_7.

\bibitem{7}
O. Schelén, \emph{Quality of Service Agents in the Internet}, Doctoral Thesis, Department of Computer Science and Electrical Engineering, Luleå University of Technology, 1998.

\bibitem{8}
I. Darmawan, M. Maulana, R. Gunawan, and N. Widiyasono, ``Evaluating Web Scraping Performance Using XPath, CSS Selector, Regular Expression, and HTML DOM With Multiprocessing,'' \emph{International Journal on Informatics Visualization}, vol. 6, no. 4, pp. 904-910, 2022.

\bibitem{9}
P.~A. David and J.~S. Shapiro, ``Community-based production of open-source software: What do we know about the developers who participate?'' \emph{Information Economics and Policy}, vol.~20, no.~3, pp. 364–398, 2008.

  \bibitem{10}
    A. Ahluwalia and S. Wani, ``Leveraging Large Language Models for Web Scraping,'' \emph{arXiv preprint arXiv:2406.08246v1}, 2023.
\bibitem{11}
A. Vaswani, N. Shazeer, N. Parmar, J. Uszkoreit, L. Jones, A. N. Gomez, Ł. Kaiser, and I. Polosukhin, ``Attention is All You Need,'' \textit{Advances in Neural Information Processing Systems (NeurIPS)}, pp. 5998--6008, 2017.
 \bibitem{12} Hadi, M. U., Tashi, Q. A., Shah, A., et al., "Large Language Models: A Comprehensive Survey of its Applications, Challenges, Limitations, and Future Prospects," TechRxiv, 2024

\bibitem{13}
Rasnayaka, S., Wang, G., Shariffdeen, R., \& Iyer, G. N. (2024). An Empirical Study on Usage and Perceptions of LLMs in a Software Engineering Project. \textit{Proceedings of the 2024 International Workshop on Large Language Models for Code (LLM4Code ’24)}, April 20, Lisbon, Portugal. ACM, New York, NY, USA \url{https://doi.org/10.1145/3643795.3648379}.
\bibitem{limitations_llms} Hadi, M. U., Tashi, Q. A., Shah, A., et al., "Large Language Models: A Comprehensive Survey of its Applications, Challenges, Limitations, and Future Prospects," TechRxiv, 2024.

\bibitem{13} Janssen, M. A. (2005). Agent-Based Modelling. \textit{Internet Encyclopaedia of Ecological Economics}, Arizona State University.

\bibitem{14} Janssen, M. A., \& Ostrom, E. (2005). Empirically based, agent-based models. Ecology and Society, 10(2), 37.



\bibitem{15} Ginart, A. A., Kodali, N., Lee, J., Xiong, C., Savarese, S., \& Emmons, J. (2024). Asynchronous Tool Usage for Real-Time Agents. Salesforce AI Research.



\bibitem{16} Ginart, A., et al. (2024). Asynchronous Agents in Real-Time AI Systems. arXiv preprint arXiv:2312.04511.

\bibitem{17}
A. Chan, K. Wei, S. Huang, N. Rajkumar, E. Perrier, S. Lazar, G. K. Hadfield, and M. Anderljung.
\newblock Infrastructure for AI Agents.
\newblock \emph{arXiv preprint arXiv:2501.10114}, 2025.

\bibitem{18}
Big Data Wire. (2024, March 6). \textit{GenAI doesn’t need bigger LLMs, it needs better data}. \url{https://www.bigdatawire.com/2024/03/06/genai-doesnt-need-bigger-llms-it-needs-better-data/}

\bibitem{19}
PrivacyOS. (2024). \textit{The 95\% of sanctions is triggered by an offense on personal data and consents}. \url{https://www.privacyos.com/en/the-95-of-sanctions-is-triggered-by-an-offense-on-personal-data-and-consents/}

\bibitem{20}
WebScraper. A brief history of web scraping. Retrieved November 5, 2024, from \url{https://webscraper.io/blog/brief-history-of-web-scraping}

\bibitem{21}
Humby, C. (2006). *Data is the new oil. It's valuable, but if unrefined it cannot really be used. It has to be changed into gas, and gasoline is used to power a car.*

\bibitem{22}
Warren S. McCulloch and Walter Pitts, 
"A logical calculus of the ideas immanent in nervous activity," 
\textit{The Bulletin of Mathematical Biophysics}, 
vol. 5, no. 4, pp. 115--133, Dec. 1943. 
DOI: \href{https://doi.org/10.1007/bf02478259}{10.1007/bf02478259}.

\bibitem{23} 
Daniel Glez-Peña, Ana Lourenço, Hugo López-Fernández, Miguel Reboiro-Jato, and Florentino Fdez-Riverola. 
\textit{Web scraping technologies in an API world}. Briefings in Bioinformatics, Vol. 15, No. 5, 788-797, 2013.

\bibitem{24}
CiteSeerX. (2024). \textit{The Growing Value of Private Data}. \url{https://citeseerx.ist.psu.edu/document?repid=rep1&type=pdf&doi=e4ae9f8b13fab5c5ce1e1e820b64bce196f60c53}

\bibitem{25}
Runacap's Ross Index. \emph{Q3 2024 Report on Fastest-Growing Open-Source Libraries}, 2024. \url{https://runacap.com/ross-index/q3-2024/}.


\bibitem{26} 
R.G.M. Morris, ``D.O. Hebb: The Organization of Behavior, Wiley: New York; 1949,'' \textit{Brain Research Bulletin}, vol. 50, no. 5-6, p. 437, Nov. 1999, doi: \href{https://doi.org/10.1016/s0361-9230(99)00182-3}{10.1016/s0361-9230(99)00182-3}.

\bibitem{27}
S. Hochreiter and J. Schmidhuber, ``Long Short-term Memory,'' \textit{Neural Computation}, vol. 9, pp. 1735-80, Dec. 1997, doi: \href{https://doi.org/10.1162/neco.1997.9.8.1735}{10.1162/neco.1997.9.8.1735}.

\bibitem{28} 
Y. Gu, L. Dong, F. Wei, and M. Huang, 
\textit{MiniLLM: Knowledge Distillation of Large Language Models}, 
Proceedings of ICLR 2024.
    
\bibitem{29}
Shreekumar, S., Mundke, S., \& Dhanawade, M. (2022). \textit{Importance of Web Scraping in E-Commerce Business}. NCRD’s Technical Review: e-Journal, 7(1). Sterling Institute of Management Studies.

 \bibitem{30}
    Z. Jiang, F. F. Xu, L. Gao, Z. Sun, Q. Liu, J. Dwivedi-Yu, Y. Yang, J. Callan, and G. Neubig, ``Active Retrieval Augmented Generation,'' \emph{arXiv preprint arXiv:2305.06983v2}, 2023.
\bibitem{hadi2024}
Hadi, M. U., Al Tashi, Q., Shah, A., et al. (2024). Large Language Models: A Comprehensive Survey of Its Applications, Challenges, Limitations, and Future Prospects. \textit{TechRxiv Preprints}. Retrieved from \url{https://doi.org/10.36227/techrxiv.23589741.v6}.


\bibitem{31}
D.~A. Tamburri, F.~Palomba, A.~Serebrenik, and A.~Zaidman, ``Discovering community patterns in open-source: A systematic approach and its evaluation,'' \emph{Empirical Software Engineering}, vol.~24, no.~3, pp. 1369–1417, 2019.

\end{thebibliography}

\end{document}
